true

### 2020-04-26 analysis/robinson2020.Rmd
getting travis working

```{r colophon-r, cache = FALSE}
# which R packages and versions?
sess <- sessionInfo()
sess$basePkgs %<>% sort()
sess$loadedOnly %<>% magrittr::extract(sort(names(sess$loadedOnly)))
if (requireNamespace("pander", quietly = TRUE)) pander::pander(sess)
```

>>>>

```{r colophon-r, cache = FALSE}
# which R packages and versions?
sess <- sessionInfo()
sess$basePkgs %<>% sort()
sess$loadedOnly %<>% magrittr::extract(sort(names(sess$loadedOnly)))
if (requireNamespace("pander", quietly = TRUE)) pander::pander(sess)

gc()
gc()
```
